### 2024-05-10 article.tex
vision cm, loss and accuracy figure now working fine

\usepackage{svg}
\usepackage{caption}
\usepackage{afterpage}
\lstdefinestyle{mystyle}{
    language=Python,
    basicstyle=\small\ttfamily,,
    keywordstyle=\color{blue},
    commentstyle=\color{green},
    stringstyle=\color{purple},
    showstringspaces=false,
    numbers=left,
    numberstyle=\tiny,
    numbersep=5pt,
    breaklines=true,
    breakatwhitespace=true,
    tabsize=2
}
\hypersetup
{
    pdfauthor   = {Zishan Siddique, Sandip Pariyar, Venus Bastola, Sushant Phagu, Binay lal Shrestha, Pravin Sangroula},	% Edit with actual author names 
}

@@

\section{Dataset Analysis}
As two mediums vision and audio are being used for classification of animals, two different datasets comprising of labeled images and labeled audio are required.
The image dataset has a total of 44 classes. Of the 44 classes, there are 31 mammals, 9 birds, and 4 reptiles. Moreover, we couldn’t find research-grade audio data for groups of animals other than birds. Thus, the audio model comprises 23 classes of birds all found in Nepal.
\subsection{Image Data from iNaturalist}
iNaturalist is an online social network of people sharing biodiversity information. It has a large size of data which includes images, audio, and video of large number of species found around the world. The data is collected by users who submit it to the site under the public domain, Creative Commons, or with all rights reserved. iNaturalist encourages its users to opt for more open licenses like Creative Commons for the research community.We collected a total of 38,442 images spanning across 44 species all found in Nepal. As the data contained some anomalous images, we had to manually remove them. After the cleaning step, the data was preprocessed as per the Efficient Net Model for better training. Of the 38,442 images collected, 50 images from each class were used as test datasets.
API provided by iNaturalist was used for downloading the data. The bar chart in Figure \ref{image_file_count_animal} shows the frequency of each class of image.
	{

		\begin{figure}
			\centering
			\includegraphics[scale=0.5]{Graphics/naturalist_horizontal.png}
			\caption{Image File count for each animal}
			\label{image_file_count_animal}
		\end{figure}

	}

\subsection{Audio Data from Xeno-canto}
Xeno-canto is a website dedicated to sharing wildlife sounds from all over the world. It provides its data under several licenses derived from Creative Commons licenses which are free for use for educational and research purposes. We collected a total of thousands of audio spanning 23 classes and performed temporal segmentation with each segment being 5 seconds long. A total of 16,230 audio files each of 5 sec was now our final dataset. Of the 16,230 audio files, 30 files for each class were used as the test dataset.
API provided by Xeno-canto was used for downloading the data. The bar chart in Figure \ref{audio_file_count_bird} shows the frequency of each class of audio.

@@

		\begin{figure}
			\centering
			\includegraphics[scale=0.5]{Graphics/xenocanto.png}
			\caption{Audio File count for each bird}
			\label{audio_file_count_bird}
		\end{figure}

@@

\subsection{EfficientNetB0}
EfficientNet is a convolutional neural network architecture and scaling method that uniformly scales all dimensions of depth/width/resolution using a compound coefficient \cite{r7}.
Unlike conventional practice that arbitrarily scales these factors, the EfficientNet scaling method uniformly scales network width, depth, and resolution with a set of fixed scaling
coefficients.
\par
\subsection{ Convolutional Neural Network}
Convolutional Neural Networks are specialized kind of neural networks for processing
data that has a grid-like topology \cite{r8}. Most machine learning libraries implement cross-correlation rather than conventionally known convolution operations in the realm of Digital
Signal Processing . In conventional multi-layer perceptrons, large number of parameters are required to learn features where as CNN uses filters to stride through whole data using a lesser number of parameters aka parameter sharing. CNNs are often applied
in large number of computer vision tasks across the industry.

@@

\begin{center}
	\captionof{table}{Overview of Results of Audio and Video Model}
	\begin{tabular}{ |c|c|c| }
		\hline
		Model  & Accuracy & F1 score \\
		\hline
		Vision & 86.1     & 86.12    \\
		\hline
		Audio  & 90.39    & 88.12    \\

		\hline
	\end{tabular}

\end{center}
\subsection{Vision Model}
The vision model was created with EfficientNetB0 as its base for transfer learning. We were able to achieve an accuracy of 86.1\% with an F1-Score of 86.12 on the test dataset. The test size of each class is 50. The following table shows the various metrics of the vision model.
\begin{center}
	\captionof{table}{Vision Model Metrics}
	\begin{tabular}{ |c|c|c| }
		\hline
		\textbf{Parameters}      & \textbf{Metrics}          \\
		\hline
		Batch Size               & 32                        \\
		\hline
		Epochs                   & 10                        \\
		\hline
		Pretrained Model         & EfficientNetB0            \\
		\hline
		Weights                  & ImageNet                  \\
		\hline
		Learning Rate            & 0.0001                    \\
		\hline
		Weight Decay             & 0.001                     \\
		\hline
		Loss Function            & Categorical Cross Entropy \\
		\hline
		Optimizer                & Adam                      \\
		\hline
		Total Parameters         & 4,063,912                 \\
		\hline
		Trainable Parameters     & 4,063,912                 \\
		\hline
		Non-Trainable Parameters & 0                         \\
		\hline
	\end{tabular}
\end{center}
\clearpage
The confusion matrix on the test dataset is shown below:

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.5]{Graphics/vision_cm.png}

	\caption{Confusion Matrix for Audio Model on test data}

\clearpage
The below figure shows the accuracy and loss of vision model:

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.65]{Graphics/accuracy_vision_model.png}
	\caption{Training and Test Accuracy of Vision Model}
	\includegraphics[scale=0.65]{Graphics/loss_vision.png}
	\caption{Training and Test Loss of Vision Model}
	\label{fig:enter-label}
\end{figure}

>>>>

\usepackage{svg}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{afterpage}
\usepackage{float}
\lstdefinestyle{mystyle}{
    language=Python,
    basicstyle=\small\ttfamily,,
    keywordstyle=\color{blue},
    commentstyle=\color{green},
    stringstyle=\color{purple},
    showstringspaces=false,
    numbers=left,
    numberstyle=\tiny,
    numbersep=5pt,
    breaklines=true,
    breakatwhitespace=true,
    tabsize=2
}
\hypersetup
{
    pdfauthor   = {Zishan Siddique, Sandip Pariyar, Venus Bastola, Sushant Phagu, Binay lal Shrestha, Pravin Sangroula},	% Edit with actual author names 
}

@@

\section{Dataset Analysis}
As two mediums vision and audio are being used for classification of animals, two different datasets comprising of labeled images and labeled audio are required.
The image dataset has a total of 44 classes. Of the 44 classes, there are 31 mammals, 9 birds, and 4 reptiles. Moreover, we couldn’t find research-grade audio data for groups of animals other than birds. Thus, the audio model comprises 23 classes of birds all found in Nepal.
\subsection{Image Data from iNaturalist}
iNaturalist is an online social network of people sharing biodiversity information. It has a large size of data which includes images, audio, and video of large number of species found around the world. The data is collected by users who submit it to the site under the public domain, Creative Commons, or with all rights reserved. iNaturalist encourages its users to opt for more open licenses like Creative Commons for the research community.We collected a total of 38,442 images spanning across 44 species all found in Nepal. As the data contained some anomalous images, we had to manually remove them. After the cleaning step, the data was preprocessed as per the Efficient Net Model for better training. Of the 38,442 images collected, 50 images from each class were used as test datasets.
API provided by iNaturalist was used for downloading the data. The bar chart in Figure \ref{image-file-count-animal} shows the frequency of each class of image.

\begin{figure}
	\centering
	\includegraphics[scale=0.5]{Graphics/naturalist_horizontal.png}
	\caption{Image File count for each animal}
	\label{image-file-count-animal}
\end{figure}

\subsection{Audio Data from Xeno-canto}
Xeno-canto is a website dedicated to sharing wildlife sounds from all over the world. It provides its data under several licenses derived from Creative Commons licenses which are free for use for educational and research purposes. We collected a total of thousands of audio spanning 23 classes and performed temporal segmentation with each segment being 5 seconds long. A total of 16,230 audio files each of 5 sec was now our final dataset. Of the 16,230 audio files, 30 files for each class were used as the test dataset.
API provided by Xeno-canto was used for downloading the data. The bar chart in Figure \ref{audio-file-count-bird} shows the frequency of each class of audio.

@@

		\begin{figure}
			\centering
			\includegraphics[scale=0.5]{Graphics/xenocanto.png}
			\caption{Audio File count for each bird}
			\label{audio-file-count-bird}
		\end{figure}

@@

\subsection{EfficientNetB0}
EfficientNet is a convolutional neural network architecture and scaling method that uniformly scales all dimensions of depth/width/resolution using a compound coefficient \cite{r7}.
Unlike conventional practice that arbitrarily scales these factors, the EfficientNet scaling method uniformly scales network width, depth, and resolution with a set of fixed scaling
coefficients.
\par
\subsection{ Convolutional Neural Network}
Convolutional Neural Networks are specialized kind of neural networks for processing
data that has a grid-like topology \cite{r8}. Most machine learning libraries implement cross-correlation rather than conventionally known convolution operations in the realm of Digital
Signal Processing . In conventional multi-layer perceptrons, large number of parameters are required to learn features where as CNN uses filters to stride through whole data using a lesser number of parameters aka parameter sharing.
% CNNs are often applied in large number of computer vision tasks across the industry.

@@

\begin{center}
	\captionof{table}{Overview of Results of Audio and Video Model}
	\begin{tabular}{ |c|c|c| }
		\hline
		Model  & Accuracy & F1 score \\
		\hline
		Vision & 86.1     & 86.12    \\
		\hline
		Audio  & 90.39    & 88.12    \\
		\hline
	\end{tabular}
\end{center}

\subsection{Vision Model}
The vision model was created with EfficientNetB0 as its base for transfer learning. We were able to achieve an accuracy of 86.1\% with an F1-Score of 86.12 on the test dataset. The following table shows the various metrics of the vision model.
\begin{center}
	\captionof{table}{Vision Model Metrics}
	\begin{tabular}{ |c|c|c| }
		\hline
		\textbf{Parameters}      & \textbf{Metrics}          \\
		\hline
		Batch Size               & 32                        \\
		\hline
		Epochs                   & 10                        \\
		\hline
		Pretrained Model         & EfficientNetB0            \\
		\hline
		Weights                  & ImageNet                  \\
		\hline
		Learning Rate            & 0.0001                    \\
		\hline
		Weight Decay             & 0.001                     \\
		\hline
		Loss Function            & Categorical Cross Entropy \\
		\hline
		Optimizer                & Adam                      \\
		\hline
		Total Parameters         & 4,063,912                 \\
		\hline
		Trainable Parameters     & 4,063,912                 \\
		\hline
		Non-Trainable Parameters & 0                         \\
		\hline
	\end{tabular}
\end{center}

The confusion matrix for vision model on the test dataset is shown in Figure \ref{cm_vision}. Figure \ref{accuracy-vision} and Figure \ref{loss-vision} shows the accuracy and loss of vision model respectively.

\begin{figure*}[t] % Use figure* for spanning both columns
	\centering
	\begin{minipage}{\textwidth} % Use minipage to ensure the figure spans the whole width
		\includegraphics[scale=0.45]{Graphics/vision_cm.png} % Replace example-image with your actual image file
		\caption{Your caption here.}
		\label{cm_vision}
	\end{minipage}
\end{figure*}

\begin{figure*}[hbt]
	\centering
	\begin{minipage}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{Graphics/accuracy_vision_model.png}
		\caption{Accuracy of Vision Model on Train and Test Data}
		\label{accuracy-vision}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=0.8\linewidth]{Graphics/loss_vision.png}
		\caption{Loss of Vision Model on Train and Test Data}
		\label{loss-vision}
	\end{minipage}
\end{figure*}
\clearpage
